---
title: "Descriptive Anaysis
author: "Maria Anthoulaki - Myrto Pieridou"
date: "2024-09-24"
output: html_document
---

```{r,echo=false}
library(dplyr)
library(tidyr)
library(ggplot2)
library(psych)
library(corrplot)
our_data = read.csv('data_all_clean.csv')

#Our data are
#Outcome :scaled_IUS_prospective:prospective intolerancec            (scaled PIU)
#sampled:number of tiles turned                                      (information sampling)
#correct_resp1:actual correct response                               (correct information)
#correct_choice:whether their final choice was correct or not        (correct choice)
#x_AG1_scaled: confidence ratings between 0-100                      (confidence)
```

General Statistics for the response variable (scaled_IUS_prospective) and the predictors we chose.

```{r}
our_data %>%
  summarise(
    mean_IUS_prospective = mean(scaled_IUS_prospective, na.rm = TRUE),   
    sd_IUS_prospective = sd(scaled_IUS_prospective, na.rm = TRUE),       
    mean_sampled = mean(sampled, na.rm = TRUE),                          
    sd_sampled = sd(sampled, na.rm = TRUE),                              
    mean_confidence = mean(x_AG1_scaled, na.rm = TRUE),                  
    sd_confidence = sd(x_AG1_scaled, na.rm = TRUE)
  )
```


Calculate mean of x_AG1_scaled (confidence), sampled and PIU by grouping age  and gender:
```{r}
# Create age groups
data = our_data %>%
  mutate(AgeGroup = cut(AgeInYears, 
                        breaks = c(0, 18, 30, 40, 50, 60, 70, Inf), 
                        labels = c("0-18", "19-30", "31-40", "41-50", "51-60", "61-70", "70+"),
                        right = FALSE))

# Calculate mean of x_AG1_scaled by age group and gender
age_gender_stats = data %>%
  group_by(AgeGroup, Gender) %>%
  summarise(
    Count = n(),
    MeanConfidence = mean(x_AG1_scaled, na.rm = TRUE),
    MeanSampled=mean(sampled,na.rm=TRUE),
    MeanPIU=mean(scaled_IUS_prospective,na.rm=TRUE),
    .groups = 'drop'
  )

# Print the summary table
print(age_gender_stats)
```

Calculate mean of x_AG1_scaled (confidence), sampled and PIU by grouping the Profilic_Pic (ID of each one)
```{r}
# Descriptive statistics grouped by subject (PROLIFIC_PIC)
data = our_data %>%
  group_by(PROLIFIC_PID) %>%
  summarise(
    mean_IUS_prospective = mean(scaled_IUS_prospective, na.rm = TRUE),
    mean_sampled = mean(sampled, na.rm = TRUE),
    mean_confidence = mean(x_AG1_scaled, na.rm = TRUE)
  )%>%
  arrange(desc(mean_confidence))

# Print the summary table
print(data)
```

Check how PIU is connected with the number of tiles the individuals open.

```{r}
data_PIU = our_data %>%
  group_by(PROLIFIC_PID) %>%
    summarise(
    mean_IUS_prospective = mean(scaled_IUS_prospective, na.rm = TRUE),
    mean_sampled = mean(sampled, na.rm = TRUE),
    mean_confidence = mean(x_AG1_scaled, na.rm = TRUE))%>% arrange(desc(mean_confidence))


data_PIU[which(data_PIU$mean_IUS_prospective >= 1.5),]
```



Then, we did some visualizations:

1) Box plot for confidence ratings (x_AG1_scaled) grouped by whether the final choice was correct     (correct_choice)

```{r}
ggplot(our_data, aes(x = factor(correct_choice), y = x_AG1_scaled)) +
  geom_boxplot(fill = "lightgreen", color = "black") +
  labs(title = "Confidence Ratings by Correct Choice", 
       x = "Correct Choice (0 = Incorrect, 1 = Correct)", 
       y = "Confidence Ratings (Scaled)") +
  theme_minimal()
```




2) Scatter plot of confidence ratings (x_AG1_scaled) by number of tiles sampled

```{r}
ggplot(our_data, aes(x = sampled, y = x_AG1_scaled)) +
  geom_point(alpha = 0.5, color = "red") +
  labs(title = "Scatter Plot of Confidence Ratings vs. Number of Tiles Sampled", 
       x = "Number of Tiles Sampled", y = "Confidence Ratings (Scaled)") +
  theme_minimal()
```

3) Plot the correlation between numeric variables in the dataset
```{r}
#Cretae the correaltion matrix
numeric_data = our_data %>% select(scaled_IUS_prospective, sampled, correct_choice, x_AG1_scaled)
correlation_matrix = cor(numeric_data, use = "complete.obs")
corrplot(correlation_matrix, method = "circle", type = "upper", tl.cex = 0.8)
```
4) Histograms of PIU, sampled and confidence
```{r}
# Histogram for scaled_IUS_prospective
hist(data$mean_IUS_prospective, 
     main = "Histogram of scaled_IUS_prospective", 
     xlab = "PIU Score", 
     col = "lightblue", 
     border = "black")

# Histogram for sampled (information sampling)
hist(data$mean_sampled, 
     main = "Histogram of Information Sampling (sampled)", 
     xlab = "Number of Tiles Turned", 
     col = "lightgreen", 
     border = "black")


# Histogram for x_AG1_scaled (confidence ratings)
hist(data$mean_confidence, 
     main = "Histogram of Confidence Ratings (x_AG1_scaled)", 
     xlab = "Confidence (0-100)", 
     col = "lightcoral", 
     border = "black")

```

5) Visualize the confidence of random people to check if we see strange patterns
```{r}
set.seed(123)  # Set seed for reproducibility (optional)
random_clients = sample(unique(our_data$PROLIFIC_PID),20)

person_sp = function(client){

person = our_data[which(our_data$PROLIFIC_PID == client), 
c("scaled_IUS_prospective", "sampled", "x_AG1_scaled", "correct_choice", "count_trial_seq")]
person = person %>% arrange(count_trial_seq)
sampled = person$sampled
correct_choice = person$correct_choice
PIU = person$scaled_IUS_prospective[1]

  
  
plot = ggplot(data = person, aes(x = count_trial_seq, y = x_AG1_scaled)) +
    geom_point() +                         
    geom_line(color = "blue") +           
    labs(x = "Count_Trial_Seq", y = "x_AG1 Scaled") + 
    theme_minimal() +                     
    ggtitle("Scatter Plot of Count_Trial_Seq vs. x_AG1 Scaled") 
  return(list(sampled = sampled, corect_choice = correct_choice, PIU = PIU,plot=plot))
}

person_sp("63bd83108d280e9d55d5e33d")
person_sp("64467f4be788c4d0c4d5ff33")
person_sp("63d7f37272879efbbf72dfb0")
person_sp("5a6759ad35f26b0001496694")
person_sp("6400da6aae94a6b881964711")
person_sp("63d3fb12ac52371a49e65860")
person_sp("5e8cb846e94a4406307d6da2")
person_sp("611d2cc49af322d296ac4117")
person_sp("5da41f84a39c100018614e31")
person_sp("6447a4bd54ab5cb19fd4beab")
person_sp("6400d8ee84822ae55ab5c542")
person_sp("5892537355550f0001509c35")
```














