---
title: "Statistical Consulting_Multilevel SEM"
author: "Myrto Piedou - s3841898"
date: "2024-11-11"
output: pdf_document
editor_options: 
  markdown: 
    wrap: 72
---

In this R file, we are going to do the analysis:

1)  Multilevel Structural Equation Modeling


GOAL: See if scaled_IUS_prospective (PIU) and x_AG1_scaled (confidence)
are mediated by sampled (information sampling)

```{r setup}
library(lavaan) 
library(psych)
library(ggplot2)
library(semPlot)
library(dplyr)
library(lme4)
library(mediation)


#Read the data
data = read.csv('C:/Users/myrto/OneDrive/Desktop/2nd year/Statistical Consulting/statisticalConsulting_docs/data_all_clean.csv')
```

Firstly, we are going to modify the dataset and select the variables
that we believe are important for the analyses.

```{r}
#Select the variables we decided that are important for the analysis
vars = c("PROLIFIC_PID",
         "sampled",
         "scaled_IUS_prospective",
         "x_AG1_scaled",
         "correct_choice",
         "count_trial_seq",
         "response_time_new_mouse_response",
         "AgeInYears", 
         "Gender")

our_data=data[,vars]
#print(our_data)
```

Chosen variables:

-> Profilic_PID = profile of each candidate sampled = number of tiles
-> turned (information sampling) scaled_IUS_prospective = PIU scaled
-> x_AG1_scaled = confidence ratings correct_choice = if their choice was
-> correct in each trial count_trial_seq = number of trial
-> response_time_new_mouse_response = seconds until he/she fill his/her
-> confidence 
-> AgeInYears = age 
-> gender = gender




1)  Multilevel Structural Equation Modeling:

Firstly we built the model with the 2 levels, which shows mediation between PIU and Confidence. This is the indirect path.
```{r}
# Define the SEM model in lavaan format

model = '
  # Level 1 (Within Subjects)  metaxi trials idiou atomou
  x_AG1_scaled ~ b1 * sampled + b2 * response_time_new_mouse_response + b3 * count_trial_seq + b4 * correct_choice
  
  # Level 2 (Between Subjects) metaxi atoma
  sampled ~ a1 * scaled_IUS_prospective + a2 * AgeInYears + a3 * Gender

  # Mediation
  indirect := a1 * b1
'

# Fit the model using lavaan with bootstrapping for indirect effects
fit = sem(model, data = our_data, cluster = "PROLIFIC_PID", se = "bootstrap", bootstrap = 100)
summary(fit, standardized = TRUE, fit.measures = TRUE)


```
Secondly, we built the model with the direct effect of PIU in confidence 
```{r}
# Define the SEM model in lavaan format

model_1 = '
  # Level 1 (Within Subjects)  metaxi trials idiou atomou
  x_AG1_scaled ~ b1 * sampled + b2 * response_time_new_mouse_response + b3 * count_trial_seq + b4 *correct_choice + b5 * scaled_IUS_prospective + b6 * AgeInYears + b7 * Gender
  

  # Mediation
  indirect := b7
'

# Fit the model using lavaan with bootstrapping for indirect effects
fit = sem(model, data = our_data, cluster = "PROLIFIC_PID", se = "bootstrap", bootstrap = 100)
summary(fit, standardized = TRUE, fit.measures = TRUE)

```




```{r}
#comparison between 2 models. For the one the response time is linear, for the other is cubic

# Linear Model
model_linear = '
  # Level 1 (Within Subjects) metaxi trials idiou atomou
  x_AG1_scaled ~ b1 * sampled + b2 * response_time_new_mouse_response + b3 * count_trial_seq + b4 * correct_choice
  
  # Level 2 (Between Subjects) metaxi atoma
  sampled ~ a1 * scaled_IUS_prospective + a2 * AgeInYears + a3 * Gender

  # Mediation
  indirect := a1 * b1
'

# Cubic Model
model_cubic = '
  # Level 1 (Within Subjects) metaxi trials idiou atomou
  x_AG1_scaled ~ b1 * sampled + b2 * response_time_new_mouse_response + b3 * count_trial_seq^3 + b4 * correct_choice
  
  # Level 2 (Between Subjects) metaxi atoma
  sampled ~ a1 * scaled_IUS_prospective + a2 * AgeInYears + a3 * Gender

  # Mediation
  indirect := a1 * b1
'

fit_linear = sem(model_linear, data = our_data, cluster = "PROLIFIC_PID", se = "bootstrap", bootstrap = 100)
fit_cubic = sem(model_cubic, data = our_data, cluster = "PROLIFIC_PID", se = "bootstrap", bootstrap = 100)

anova(fit_linear, fit_cubic)


```






